---
title: "Multiple Linear Regression of Advertising Data"
author: "Alexander Lee"
date: "October 14, 2016"
output: pdf_document
---

#Abstract

This report seeks to replicate the research found in *Simple Linear Regression*, chapter 3 of the book **An Introduction to Statistical Learning** by Gareth James, et al., on a set of advertising data. I run a multiple linear regression on the data and create various functions to calculate several statistics, including the residual square error and the F-statistic.

#Introduction

The goal of this research is to use existing data to formulate a marketing plan that will result in higher product sales. To that end, we will run a multiple linear regression to model the increase of sales against the amount of money spent on marketing the product through various media - TV, radio, and newspapers. We will analyze this to determine how advertising affects sales, and how the company should budget for advertising in order to increase sales of the product.

#Data
The Advertising data set consists of the `Sales` (in thousands of units) of a particular product in 200 different markets, along with advertising budgets (in thousands of dollars) for the product in each of those markets for three different media: `TV`, `Radio`, and `Newspaper`. 

```{r echo=FALSE,warning=FALSE}
library(xtable)
load('../data/regression.RData')
head(advertising)
```

#Methodology

We perform a simple linear regression on `Sales` for each of the three other factors, under the model:

`Sales = a + b * (FACTOR)`

Where `(FACTOR)` is either `TV`, `Radio`, or `Newspaper`. We predict there to be a linear relationship between `Sales` and the amount of budget placed in advertising for each of these three media.

```{r echo=FALSE,warning=FALSE}
tv_reg <- lm(Sales ~ TV, data = advertising)
radio_reg <- lm(Sales ~ Radio, data = advertising)
newspaper_reg <- lm(Sales ~ Newspaper, data = advertising)

tv_reg_summary <- summary(tv_reg)
radio_reg_summary <- summary(radio_reg)
newspaper_reg_summary <- summary(newspaper_reg)

tv_reg_xtable <- xtable(tv_reg_summary$coefficients,
                        caption = "Summary of Simple Linear
                        Regresssion on TV")
radio_reg_xtable <- xtable(radio_reg_summary$coefficients,
                           caption = "Summary of Simple Linear
                           Regression on Radio")
newspaper_reg_xtable <- xtable(newspaper_reg_summary$coefficients,
                               caption = "Summary of Simple Linear
                               Regression on Newspaper")
```


```{r xtable1, results='asis',echo=FALSE,comment=''}
print(tv_reg_xtable)
```
```{r xtable2, results='asis',echo=FALSE,comment=''}
print(radio_reg_xtable)
```
```{r xtable3, results='asis',echo=FALSE,comment=''}
print(newspaper_reg_xtable)
```


Next, we look at the relationship between `Sales` and the budgets of the various forms of media using the model:

    `Sales = a + b * TV + c * Radio + d * Newspaper`

That is, we predict there to be a relationship between the amount of money spent on TV, Radio, and Newspaper advertising and the number of sales of units. We approximate the values of a, b, c, and d using a multiple linear regression under the least squares criterion.

#Results

We computed the correlation coefficients using the lm() function, with `TV` as a function of `Sales`. 

```{r echo=FALSE,comment=''}
ad_reg <- lm(Sales ~ TV + Radio + Newspaper, data = advertising)
ad_reg_summ <- summary(ad_reg)
ad_reg_xtable <- xtable(ad_reg_summ$coefficients,
                        caption = "Summary of Coefficients
                        for All Independent Factors")
ad_intercept <- ad_reg_summ$coefficients["(Intercept)", "Estimate"]
ad_tv <- ad_reg_summ$coefficients["TV", "Estimate"]
ad_radio <- ad_reg_summ$coefficients["Radio", "Estimate"]
ad_newspaper <- ad_reg_summ$coefficients["Newspaper", "Estimate"]

source('../code/functions/regression-functions.R')
```


```{r xtable4, results='asis',echo=FALSE,comment=''}
print(ad_reg_xtable)
```


The estimates of these coefficients, a, b, c, and d, are $`r ad_intercept`$, $`r ad_tv`$, $`r ad_radio`$, and $`r ad_newspaper`$, respectively. For every $1,000 increase in spending on TV advertising, sales are projected to increase by $`r ad_tv / 1000`$ units; this means that units have to cost at least $`r round(1000 / ad_tv, 2)`$ in order to be profitable. For every $1,000 increase in spending on Radio advertising, sales are projected to increase by $`r ad_radio / 1000`$ units; this means that units have to cost at least $`r round(1000 / ad_radio, 2)`$ in order to be profitable. For every $1,000 increase in spending on Newspaper advertising, sales are projected to increase by $`r ad_newspaper / 1000`$ units. 

```{r comment='',echo=FALSE}
ad_df <- data.frame("values" = c(r_squared(ad_reg), residual_std_error(ad_reg), f_statistic(ad_reg)),row.names = c("R^2", "RSE", "F-statistic"))
ad_df_xtable <- xtable(ad_df, caption = "Regression Statistics")
```

```{r xtable5, results='asis',echo=FALSE,comment=''}
print(tv_reg_xtable)
```


On average, sales data will deviate from the true regression model by $`r round(residual_std_error(ad_reg), 4)`$ units. An R^2^ of $`r round(r_squared(ad_reg), 4)`$ means $`r round(r_squared(ad_reg), 4) * 100`$% of the variability is explained by the model. An F-statistic of $`r round(f_statistic(ad_reg), 4)`$ means that the coefficients found by our model are very likely to be close to the true regression values.



#Conclusions

Individually, each of the factors `TV`, `Radio`, and `Newspaper` have a significant effect on the number of `Sales`. Together, only `TV` and `Radio` have significant effects; an increase in `Newspaper` budget actually decreases the number of `Sales`.

There is a positive correlation between the budget for TV advertising and Sales; however, this relationship is very minimal. For every $1,000 spent on advertising only another 48 units are sold, so each unit would have to cost at least $20.84 in order to break even or profit off the units sold. 
