---
title: "Multiple Linear Regression of Advertising Data"
author: "Alexander Lee"
date: "October 14, 2016"
output: pdf_document
---

#Abstract

This report seeks to replicate the research found in *Simple Linear Regression*, chapter 3 of the book **An Introduction to Statistical Learning** by Gareth James, et al., on a set of advertising data. I run a multiple linear regression on the data and create various functions to calculate several statistics, including the residual square error and the F-statistic.

#Introduction

The goal of this research is to use existing data to formulate a marketing plan that will result in higher product sales. To that end, we will run a multiple linear regression to model the increase of sales against the amount of money spent on marketing the product through various media - TV, radio, and newspapers. We will analyze this to determine how advertising affects sales, and how the company should budget for advertising in order to increase sales of the product.

#Data

The Advertising data set consists of the `Sales` (in thousands of units) of a particular product in 200 different markets, along with advertising budgets (in thousands of dollars) for the product in each of those markets for three different media: `TV`, `Radio`, and `Newspaper`. 

```{r echo=FALSE,warning=FALSE}
library(xtable)
load('../data/regression.RData')
head(advertising)
```

#Methodology

We perform a simple linear regression on `Sales` for each of the three other factors, under the model:

`Sales = a + b * (FACTOR)`

Where `(FACTOR)` is either `TV`, `Radio`, or `Newspaper`. We predict there to be a linear relationship between `Sales` and the amount of budget placed in advertising for each of these three media. The summaries of these can be found in Tables 1-3.

```{r echo=FALSE,warning=FALSE}
tv_reg <- lm(Sales ~ TV, data = advertising)
radio_reg <- lm(Sales ~ Radio, data = advertising)
newspaper_reg <- lm(Sales ~ Newspaper, data = advertising)

tv_reg_summary <- summary(tv_reg)
radio_reg_summary <- summary(radio_reg)
newspaper_reg_summary <- summary(newspaper_reg)

tv_reg_xtable <- xtable(tv_reg_summary$coefficients,
                        caption = "Summary of Simple Linear
                        Regresssion on TV")
radio_reg_xtable <- xtable(radio_reg_summary$coefficients,
                           caption = "Summary of Simple Linear
                           Regression on Radio")
newspaper_reg_xtable <- xtable(newspaper_reg_summary$coefficients,
                               caption = "Summary of Simple Linear
                               Regression on Newspaper")
```


Next, we look at the relationship between `Sales` and the budgets of the various forms of media using the model:

    `Sales = a + b * TV + c * Radio + d * Newspaper`

That is, we predict there to be a relationship between the amount of money spent on `TV`, `Radio`, and `Newspaper` advertising and the number of sales of units. We approximate the values of `a`, `b`, `c`, and `d` using a multiple linear regression under the least squares criterion.

#Results

We computed the correlation coefficients using the lm() function, with `TV` as a function of `Sales`. The summaries of the coefficients can be found in Table 4.

```{r echo=FALSE,comment=''}
ad_reg <- lm(Sales ~ TV + Radio + Newspaper, data = advertising)
ad_reg_summ <- summary(ad_reg)
ad_reg_xtable <- xtable(ad_reg_summ$coefficients,
                        caption = "Summary of Coefficients
                        for All Independent Factors")
ad_intercept <- ad_reg_summ$coefficients["(Intercept)", "Estimate"]
ad_tv <- ad_reg_summ$coefficients["TV", "Estimate"]
ad_radio <- ad_reg_summ$coefficients["Radio", "Estimate"]
ad_newspaper <- ad_reg_summ$coefficients["Newspaper", "Estimate"]

source('../code/functions/regression-functions.R')
```


The correlations between each of the factors can be found in Table 5. A correlation closer in absolute value to 1 means that a change in one variable definitively predicts a change in the other.

```{r echo=FALSE}
load('../data/correlation-matrix.RData')
cor_xtable <- xtable(correlation, 
                     caption = "Correlation Matrix of the
                     Multiple Linear Regression")
```



The estimates of these coefficients, a, b, c, and d, are $`r round(ad_intercept, 4)`$, $`r round(ad_tv, 4)`$, $`r round(ad_radio, 4)`$, and $`r round(ad_newspaper, 4)`$, respectively. For every $1,000 increase in spending on TV advertising, sales are projected to increase by $`r round(ad_tv * 1000)`$ units; this means that units have to cost at least $ $`r round(1 / ad_tv, 2)`$ in order to be profitable. For every $1,000 increase in spending on Radio advertising, sales are projected to increase by approximately $`r round(ad_radio * 1000)`$ units; this means that units have to cost at least $ $`r round(1 / ad_radio, 2)`$ in order to be profitable. For every $1,000 increase in spending on Newspaper advertising, sales are projected to increase by $`r round(ad_newspaper * 1000)`$ units. 


```{r comment='',echo=FALSE}
ad_df <- data.frame("values" = c(r_squared(ad_reg), residual_std_error(ad_reg), f_statistic(ad_reg)),row.names = c("R^2", "RSE", "F-statistic"))
ad_df_xtable <- xtable(ad_df, caption = "Regression Statistics")
```



Various statistics of the regression can be found in Table 6. On average, sales data will deviate from the true regression model by $`r round(residual_std_error(ad_reg), 4)`$ units. An R^2^ of $`r round(r_squared(ad_reg), 4)`$ means $`r round(r_squared(ad_reg), 4) * 100`$% of the variability is explained by the model. An F-statistic of $`r round(f_statistic(ad_reg), 4)`$ means that the coefficients found by our model are very likely to be close to the true regression values.



#Conclusions

Individually, each of the factors `TV`, `Radio`, and `Newspaper` have a significant effect on the number of `Sales`. Together, only `TV` and `Radio` have significant effects; an increase in `Newspaper` budget actually decreases the number of `Sales`.

Assuming the units are priced higher than those stated above, it would be wise to increase advertising in those media for which an increase in advertising would lead to profit (after subtracting the cost of advertising). 

#Figures

```{r xtable1, results='asis',echo=FALSE,comment=''}
print(tv_reg_xtable)
```
```{r xtable2, results='asis',echo=FALSE,comment=''}
print(radio_reg_xtable)
```
```{r xtable3, results='asis',echo=FALSE,comment=''}
print(newspaper_reg_xtable)
```
```{r xtable4, results='asis',echo=FALSE,comment=''}
print(ad_reg_xtable)
```
```{r xtable5, results='asis',echo=FALSE,comment=''}
print(cor_xtable)
```
```{r xtable6, results='asis',echo=FALSE,comment=''}
print(ad_df_xtable)
```